
\begin{abstract}

Rather than the expected market flattening by digital advances, market centralization is being witnessed in many data-driven economic markets, such as aggregators, social media markets, e-commerce, and search engines. The control over personal data, at the intersection of personal privacy and commercial assets, shapes market competition to foster market dominance in subtle ways. To restore a fair distribution of power, the European data protection regulation sets data minimization as the general benchmark, but the legal and technical framework for achieving this target is left open. This work proposes a GDPR-compliant tool to improve effective market competition from legal and technical data minimization. We demonstrate the value of our proposal and draw conclusions on theoretical and practical analysis.

\begin{comment}
The WOPA subject is trade secrets and personal data. The key link is personal data, so our idea is to enhance privacy protection and effective competition in the marketplace by contributing to the realization of data minimization. The significance of personal data minimization for privacy protection lies in reducing the collection of unnecessary information as well as in reducing the direct link between data and data subjects. The impact of personal data minimization on effective competition in the market can be explored in terms of the control of personal data by platforms, the freedom of user choice, and the flow of personal data. This section will cover the relationship between personal data and trade secrets and how the market will be affected if personal data is considered a trade secret. Following " as open as possible, as closed as necessary", all rules for personal data need to find the right place between privacy protection and data sharing. Data sharing hides the economic and market value of personal data. I think this is why the WOPA topic is trade secrets and personal data. We don't think frameworks and tools concerned solely with privacy or economic efficiency can be realized from paper to reality. A meaningful framework needs to consider both, and that is exactly what we are trying to do.
\end{comment}

\end{abstract}
